---
title: "Analyse"
author: "GARBA Moussa"
date: "2/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r }
#install.packages("VIM")
#install.packages("VIM", dependencies = TRUE)
#install.packages("naniar")
#install.packages("missMDA")
#install.packages("Amelia")
#install.packages("mice")
#install.packages("missForest")
#install.packages("FactoMineR")

#install.packages("DescTools")
```




```{r }
library(readxl)
library(tidyverse)
library(naniar)
library(FactoMineR)
library(missMDA)
library(SnowballC) # for stemming
library(readxl) # for read xlsx file 
library(scales)
library(plotly)
library(kableExtra)
library(ggpubr)
library(corrr)
library(DataExplorer)
library(SmartEDA)



library(broom)

library(stringr)
library(lubridate)
library(ggforce)
library(reshape2)

library(corrplot)
library(lattice)
library(lava)
library(caret)





```


#1. Data exploration 

##1.1 Data 


## import data 
```{r}
 
data_ex5  <- read_excel("/Users/garbamoussa/Desktop/Bureau/R/Education_Data/Data/Excel_Annex.xlsx", sheet = "Ex5")

```


## print shortly some rows  


```{r}
glimpse(data_ex5)
```


```{r }
head(data_ex5)
```


## Replace % by Percent 
```{r}
data_ex5 <- data_ex5 %>%
   rename_all(.funs = funs(sub("%", "Percent", names(data_ex5)))) 

```


## Remove Whispace into columns names 
```{r}

data_ex5 %>%  
  select_all(~gsub("\\s+|\\.", "_", .)) %>% 
  select_all(tolower)

```

```{r}
names(data_ex5) <- gsub(" ", "_", names(data_ex5))
        
```


## Missing value analysis 
   
```{r}

# Overview of the data - Type = 1
ExpData(data=data_ex5,type=1)

# Structure of the data - Type = 2
ExpData(data=data_ex5,type=2)

```

## disctinct value into each column by class

```{r }
#the map_df function combines the data frames row-wise into a single data frame.

data_ex5 %>% map_df(~(data.frame(n_distinct = n_distinct(.x),
                                  class = class(.x))))
``` 

## Unique value into each categorical variables 

```{r }
unique(data_ex5[c("Region", "Location", "School_Type")])

```



## Number missing value by each column 


```{r}
gg_miss_var(data_ex5)
```




##  percentage of missing value in the data. 
```{r}
 
pct_miss(data_ex5)
```




```{r }
sapply(data_ex5, function(x) sum(is.na(x)))
```

## number of missing values in the  

```{r}
n_miss(data_ex5) 
```



## Data shape without missing value

```{r}
n_complete(data_ex5) 
```


## Number of missing value for Water variable 

```{r}
n_miss(data_ex5$Water)
```


## Display each missing value by row 

```{r}
as_shadow(data_ex5)
```




```{r}
bind_shadow(data_ex5)
```


# Plot with missing values


```{r}
data_ex5 %>%
  group_by(data_ex5$Region) %>%
  miss_var_summary()
```




```{r}
data_ex5 %>%
  bind_shadow() %>%
  group_by(Region) %>%
  summarise_at(.vars = "Location",
               .funs = c("mean", "sd", "var", "min", "max"),
               na.rm = TRUE)
```

## Descrition statistique for Learning achievement score 


```{r}
data_ex5 %>%
  bind_shadow() %>%
  group_by(Region) %>%
  summarise_at(.vars = "Learning_achievement_score",
               .funs = c("mean", "sd", "var", "min", "max"),
               na.rm = TRUE)


```

## Summary description statistique for each variable 

```{r }
summary(data_ex5)
```

## Convert each categorical variable to factor 

```{r }
data_ex5$Region   = as.factor(data_ex5$Region)
data_ex5$Location   = as.factor(data_ex5$Location)
data_ex5$School_Type  = as.factor(data_ex5$School_Type)

```


## Plot percentage for missing value for each variable 
```{r}
vis_miss(data_ex5, sort_miss = TRUE) 
```



## Plot by facet Region for Electricity and Water 
```{r}
ggplot(data_ex5, 
       aes(x = Electricity, 
           y = Water)) + 
  geom_miss_point() + 
  facet_wrap(~data_ex5$Region)+ 
  theme_dark()

```

## Electricity density 

```{r}
ggplot( bind_shadow(data_ex5),
       aes(x = Electricity,
           fill = Water)) + 
  geom_density(alpha=0.5)
```




```{r}
ggplot( bind_shadow(data_ex5),
       aes(x = Electricity,
           fill = Toilets)) + 
  geom_density(alpha=0.5)
```

# Histogram for dropout rate 

```{r}
## example d'une graphique permettant de representer l'histogramme d'une variable 
ggplot(data_ex5) + geom_histogram(aes(x = Dropout_rate), fill="darkgreen")
```

## Bar plot for Region 
```{r}
ggplot(data_ex5) + geom_bar(aes(x = Region),color = "black", fill="darkgreen")
```


## Number of dropout rate for each region 

```{r}
ggplot(data_ex5) + geom_bar(aes(x = Dropout_rate, y = Region), stat = "identity")

```

## Relationship between Electricity and Dropout_rate for each region 
```{r}
# Scatterplot
ggplot(data_ex5, aes(x=Electricity, y=Dropout_rate)) + 
  geom_point(aes(col=Region, size=Water)) + 
  geom_smooth(method="loess", se=F) + 
  xlim(c(0, 1)) + 
  ylim(c(-50, 50)) + 
  labs(subtitle="Electricity Vs Dropout_rate", 
       y="Dropout_rate", 
       x="Electricity", 
       title="Relationship between Electricity and Dropout_rate", 
       caption = "Source: Education data")

```


```{r }
# remove dropout rate into dataframe 
df = subset(data_ex5, select = -c(Dropout_rate))

# Identifier les variables numériques 
numericData <- df[sapply(df, is.numeric)]

#correlation 
descrCor <- cor(numericData, use="pairwise.complete.obs")
#descrCor <-  max(descrCor,na.rm=TRUE)
# display matrice correlation 
print(descrCor)
```


## coorplot  for independant variables 


```{r }
# Visualize Correlation Matrix
corrplot(descrCor, order = "FPC", method="number", type = "lower", tl.cex = 0.7, tl.col = rgb(0, 0, 0))


#corrplot(cor(df), order = "FPC", method = "color", type = "lower", tl.cex = 0.7, tl.col = rgb(0, 0, 0))
```




```{r }

corrplot(descrCor, type="upper", order="hclust", tl.col="black", tl.srt=45)
```


## Remove NA values 

```{r }
data_ex5<-na.omit(data_ex5)

```




```{r }
# Checking Variables that are highly correlated
highlyCorrelated = findCorrelation(descrCor, cutoff=0.7)

#Identifying Variable Names of Highly Correlated Variables
highlyCorCol = colnames(numericData)[highlyCorrelated]

#Print highly correlated attributes
highlyCorCol


#Remove highly correlated variables and create a new dataset
dat3 = df[, -which(colnames(df) %in% highlyCorCol)]
dim(dat3)



```





```{r }
#Build Linear Regression Model
fit = lm(Dropout_rate ~ ., data=data_ex5)

#Check Model Performance
summary(fit)

#Extracting Coefficients
summary(fit)$coeff
anova(fit)

par(mfrow=c(2,2))
plot(fit)
```


```{r }

anova(fit)
```


Region, Location
School Type
Water 
Electricity
Toilets
Sanitary towels for girl 
Percent classrooms With Black Booards

Pupil Teacher Ratio 
Class Size
Percent student with English Textbook 
Percent student with Math Textbook 
2018_Percent_repeaters
Repetition_rate
Orphans_Prim 


```{r }

summary(fit)$r.squared
summary(fit)$adj.r.squared
AIC(fit)
BIC(fit)
```




```{r }
require(MASS)
require(boot.StepAIC)
step <- stepAIC(fit, direction="both")
summary(step)


```


```{r }
step <- stepAIC(fit, direction="backward")
summary(step)

```



```{r }
step <- stepAIC(fit, direction="forward")
summary(step)
```


```{r }
#Stepwise Selection with BIC
n = dim(data_ex5)[1]
stepBIC = stepAIC(fit,k=log(n))
summary(stepBIC)
```


```{r }
library(car)
#Autocorrelation Test
#durbinWatsonTest(stepBIC)
dwtest(stepBIC)

#Normality Of Residuals (Should be > 0.05)
res=residuals(stepBIC,type="pearson")
shapiro.test(res)

#Testing for heteroscedasticity (Should be > 0.05)
ncvTest(stepBIC)

#Outliers – Bonferonni test
outlierTest(stepBIC)

#See Residuals
resid = residuals(stepBIC)

#Relative Importance
install.packages("relaimpo")
library(relaimpo)
calc.relimp(stepBIC)

```
```{r }

#See Predicted Value
pred = predict(stepBIC,data_ex5)
#See Actual vs. Predicted Value
finaldata = cbind(data_ex5,pred)
print(head(subset(finaldata, select = c(Dropout_rate,pred))))

```




```{r }
#Calculating RMSE
rmse = sqrt(mean((data_ex5$Dropout_rate - pred)^2))
print(rmse)

```

```{r }
#K-fold cross-validation
library(DAAG)
kfold = cv.lm(data=data_ex5, stepBIC, m=5)
```



```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```



```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```



```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```

